\section{BI\&A Applications: From Big Data to Big Impact}

This chapter describes new streams where business intelligence and analytics big data will be used. Streams like international travel, high-speed network connections, global supply-chain, and
outsourcing have created a tremendous opportunity for IT
advancement. It predicted by Thomas Freeman in his seminal
book, The World is Flat (2005).

Several global business and IT trends have helped shape past
and present BI\&A research directions. In addition to ultra-fast
global IT connections, the development and deployment of
business-related data standards, electronic data interchange
(EDI) formats, and business databases and information
systems have greatly facilitated business data creation and
utilization. The development of the Internet in the 1970s and
the subsequent large-scale adoption of the World Wide Web
since the 1990s have increased business data generation and
collection speeds exponentially. Recently, the Big Data era
has quietly descended on many communities, from governments
and e-commerce to health organizations. With an
overwhelming amount of web-based, mobile, and sensorgenerated
data arriving at a terabyte and even exabyte scale
(The Economist 2010a, 2010b), new science, discovery, and
insights can be obtained from the highly detailed, contextualized,
and rich contents of relevance to any business or
organization.

In addition to being data driven, BI\&A is highly applied and
can leverage opportunities presented by the abundant data and
domain-specific analytics needed in many critical and highimpact
application areas. Several of these promising and
high-impact BI\&A applications are presented below, with a
discussion of the data and analytics characteristics, potential
impacts, and selected illustrative examples or studies: (1) ecommerce
and market intelligence, (2) e-government and
politics 2.0, (3) science and technology, (4) smart health and
well-being, and (5) security and public safety. By carefully
analyzing the application and data characteristics, researchers
and practitioners can then adopt or develop the appropriate
analytical techniques to derive the intended impact. IS departments thus face unique opportunities and
challenges in developing integrated BI\&A research and
education programs for the new generation of data/analyticssavvy
and business-relevant students and professionals (Chen
2011a).

In conclusion to technical system implementation, significant business
or domain knowledge as well as effective communication
skills are needed for the successful completion of such BI\&A
projects.