
% April 2, 2018

% Translate

\bibitem{Miller:2012a}
	Miller, K. 2012a. <<Big Data Analytics in Biomedical Research,>>
	Biomedical Computation Review (available at http://biomedicalcomputationreview.org/content/big-data-analyticsbiomedical-research;
	accessed April 2, 2018).

\bibitem{Gelfand:2012}
	Gelfand, A. 2011/2012. “Privacy and Biomedical Research:
	Building a Trust Infrastructure—An Exploration of Data-Driven
	and Process-Driven Approaches to Data Privacy,” Biomedical
	Computation Review, Winter, pp. 23-28 (available at http://biomedicalcomputationreview.org/content/privacy-andbiomedical-research-building-trust-infrastructure, 
	accessed
	April 2, 2018).
	
\bibitem{Lin:2011}	
	Lin, Y., Brown, R. A., Yang, H. J., Li, S., Lu, H., and Chen, H.
	2011. “Data Mining Large-Scale Electronic Health Records for
	Clinical Support,” IEEE Intelligent Systems (26:5), pp. 87-90
	
\bibitem{Miller:2012b}	
	Miller, K. 2012b. “Leveraging Social Media for Biomedical
	Research: How Social Media Sites Are Rapidly Doing Unique
	Research on Large Cohorts,” Biomedical Computation Review
	(available at http://biomedicalcomputationreview.org/content/
	leveraging-social-media-biomedical-research; accessed August
	2, 2012).

\bibitem{Wactlar:2011}		
	Wactlar, H., Pavel, M., and Barkis, W. 2011. “Can Computer
	Science Save Healthcare?” IEEE Intelligent Systems (26:5), pp.
	79-83.
	
\bibitem{Chen:2011b}
	Chen, H. 2011b. “Smart Health and Wellbeing,” IEEE Intelligent
	Systems (26:5), pp. 78-79.

\bibitem{Chen:2006}	
	Chen, H. 2006. Intelligence and Security Informatics for International
	Security: Information Sharing and Data Mining, New
	York: Springer.

\bibitem{Perlroth:2012}		
	Perlroth, N., and Rusli, E. M. 2012. “Security Start-Ups Catch
	Fancy of Investors,” New York Times, Technology Section,
	August 5.

\bibitem{Brantingham:2011}		
	Brantingham, P. L. 2011. “Computational Criminology,” Keynote
	Address to the European Intelligence and Security Informatics
	Conference, Athens, Greece, September 12-14.
	
\bibitem{Salton:1989}	
	Salton, G. 1989. Automatic Text Processing, Reading, MA:
	Addison Wesley

\bibitem{Blei:2012}
	Blei, D. M. 2012. “Probabilistic Topic Models,” Communications
	of the ACM (55:4), pp. 77-84.
	
\bibitem{Maybury:2004}
	Maybury, M. T. (ed.). 2004. New Directions in Question
	Answering, Cambridge, MA: The MIT Press.
	
\bibitem{Pang:2008}	
	Pang, B., and Lee, L. 2008. “Opinion Mining and Sentiment
	Analysis,” Foundations and Trends in Information Retrieval
	(2:1-2), pp. 1-135.
	
\bibitem{Manning:1999}	
	Manning, C. D., and Schütze, H. 1999. Foundations of Statistical
	Natural Language Processing, Cambridge, MA: The MIT Press.
	
\bibitem{OReilly:2005}		
	O’Reilly, T. 2005. “What Is Web 2.0? Design Patterns and
	Business Models for the Next Generation of Software,”
	September 30, (http://www.oreillynet.com/pub/a/oreilly/tim/
	news/2005/09/30/what-is-web-20.html).
	
\bibitem{Schonfeld:2005}
	Schonfeld, E. 2005. “The Great Giveaway,” Business 2.0 (6:3), pp.
	80-86.




